---
title: "analysis1"
author: "Miklos Bognar"
date: "2023-01-13"
output: html_document
---

# Source to raw
## Load packages for this section
```{r message=F}
library(tidyverse)
library(papaja)
library(lme4)
library(lmerTest)
library(rstatix)
library(BayesFactor)
library(readtext)
```

## Loading data
```{r}
hun_data = read_csv("data/hun_data.csv")
it_data = read_csv("data/it_data.txt")

source_data = rbind(hun_data,it_data)
source_data = source_data %>% 
  group_by(participant_id) %>% 
  mutate(id = cur_group_id()) %>% 
  ungroup()


```

## Demographic analysis
---------------------------

## Prepare for sequential analysis
### Use only response data
```{r}
raw_data = source_data %>%
  filter(is.na(block)) %>%
  filter(task == "response")
  

```

### Check all the conditions with mean RT
```{r}
raw_data %>% 
  group_by(congruency) %>% 
  summarize(N = n(),
            mean_rt = mean(as.numeric(rt), na.rm = T)) %>% 
  ungroup()
```

### Create a numeric id from 
```{r}
raw_data = raw_data %>%
  group_by(participant_id) %>% 
  mutate(id = cur_group_id()) %>% 
  ungroup()
```

### Create previous trial data
```{r}
raw_data = raw_data %>% 
  arrange(participant_id, as.numeric(trial_index)) %>% 
  mutate(previous_rt = lag(rt),
         previous_congruency = lag(congruency),
         previous_correct = lag(correct))
  
```

### Create rt and accuracy data
```{r}
raw_rt = raw_data %>% 
  filter(correct == T,
         previous_correct == T,
         previous_rt > 0)
```

```{r}
raw_accuracy = raw_data %>% 
  filter(previous_correct == T) %>% 
  mutate(acc = ifelse(correct==T, 1,0))
```
--------------------
### Outlier detection
```{r}
rt_conditional_means = raw_rt %>% 
  group_by(id,congruency, previous_congruency) %>% 
  summarize(conditional_mean = mean(as.numeric(rt), na.rm = T),
            conditional_sd = sd(as.numeric(rt), na.rm=T))
  
raw_rt = raw_rt %>% 
  left_join(.,rt_conditional_means, by=c("id","congruency","previous_congruency"))


raw_rt = raw_rt %>% 
  mutate(rt = as.numeric(rt))

raw_rt = raw_rt %>% 
  mutate(rt_z = (rt-conditional_mean)/conditional_sd) %>% 
  mutate(drop_outlier = ifelse(abs(rt_z)>=3,1,0))


filtered_rt = raw_rt %>% 
  filter(drop_outlier == 0)
```



```{r}
### Check cse without outlier detection```{r}
cse_rt_data = filtered_rt %>% 
  group_by(congruency, previous_congruency) %>% 
  summarize(N = n(),
            mean_rt = mean(as.numeric(rt), na.rm = T),
            sd_rt = sd(rt, na.rm = T),
            se_rt = sd_rt/sqrt(N))
```

```{r}
cse_rt_plot = cse_rt_data %>% 
  ggplot()+
  aes(x=factor(previous_congruency, level=c("no_conflict","low_conflict", "high_conflict")), y=mean_rt, color=congruency, group=congruency)+
  geom_point(size=2)+
  geom_path(size=1)+
  geom_errorbar(size=1,aes(ymin=mean_rt-se_rt,
                    ymax=mean_rt+se_rt,
                    width=.2))+
  papaja::theme_apa()+
  labs(x="Previous Congruency",
       y= "Reaction time",
       color="Current Congruency",
       title="Pilot CSE plot")



cse_rt_plot
```

```{r}
mymodel = lmer(rt ~ congruency * previous_congruency + (1|id), data=filtered_rt)
summary(mymodel)
anova(mymodel)

no_interaction_model = lmer(rt ~ congruency + previous_congruency + (1|id), data=filtered_rt)
anova(no_interaction_model)

anova(no_interaction_model, mymodel)

no_effect_model = lmer(rt ~ (1|id), data=filtered_rt)

summary(no_effect_model)
```
# Accuracy analysis with plot
```{r}
cse_acc_data = raw_accuracy %>% 
  group_by(congruency, previous_congruency) %>% 
  summarize(N = n(),
            mean_acc = mean(acc, na.rm = T),
            sd_acc = sd(acc, na.rm = T),
            se_acc = sd_acc/sqrt(N))
```
```{r}
cse_acc_plot = cse_acc_data %>% 
  ggplot()+
  aes(x=factor(previous_congruency, level=c("no_conflict","low_conflict","high_conflict")), y=mean_acc, color=congruency, group=congruency)+
  geom_point(size=2)+
  geom_path(size=1)+
  geom_errorbar(size=1,aes(ymin=mean_acc-se_acc,
                    ymax=mean_acc+se_acc,
                    width=.2))+
  papaja::theme_apa()+
  labs(x="Previous Congruency",
       y= "Mean accuracy",
       color="Current Congruency",
       title="Pilot CSE plot - Accuracy")



cse_acc_plot
```
```{r}
mymodel_acc = lmer(acc ~ congruency * previous_congruency + (1|id), data=raw_accuracy)
summary(mymodel_acc)
anova(mymodel_acc)
```
```{r}
pairwise_t_test(filter(raw_accuracy, congruency=="low_conflict"), acc ~ previous_congruency, p.adjust.method = "bonferroni")
pairwise_t_test(filter(raw_accuracy, congruency=="no_conflict"), acc ~ previous_congruency, p.adjust.method = "bonferroni")
```